---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
load packages
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(lme4)
library(lmerTest)
library(MuMIn) #rsquared
library(emmeans)
library(wesanderson)
library(effects)
```

Environmental variables(sol depth etc) at bottom of script

load foliar data and predictors
```{r}
needs = read.csv("foliar.csv")
preds = read.csv("PerdyPred.csv")
```

changing treatment factor names
```{r}
needs$trt = factor(needs$trt, levels = c("U", "T", "S"), labels= c("Unburned", "Burned", "Subsided"))
preds$trt = factor(preds$trt, levels = c("unburned", "burn", "burn/sub"), labels= c("Unburned", "Burned", "Subsided"))

fol = merge(needs, preds, by = c("site", "trt", "plot"))
```

N models
```{r}
m1 <-lmer(n ~ trt + (1|site/plot), na.action=na.exclude, data = fol)
m2 <-lmer(n ~ 1  + (1|site/plot), na.action=na.exclude, data = fol)
anova(m2, m1)
anova(m1)

plot(m1)
r.squaredGLMM(m1)
summary(m1)
```
N
means and contrasts
```{r}
fol.trt =  emmeans(m1, "trt")
pairs(fol.trt)
emmeans(m1, "trt")
plot(fol.trt, comparisons = TRUE)
```

graph N
```{r}
plot(allEffects(m1))
trt.eff <- Effect(c("trt"), m1, xlevels=500)
trt.eff=as.data.frame(trt.eff)

#home made box plot
ggplot(trt.eff, aes(x=trt, fit, color=trt, fill = trt)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
   geom_jitter(data=fol, aes(x = trt, y= n, fill = trt, color =  trt), alpha = 0.2, width = 0.1) +
  xlab("Disturbance catagory") +
  ylab("Nitrogen (%)") +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))

#bar plot
ggplot(trt.eff, aes(x=trt, fit, fill = trt)) +  
  geom_bar(stat = "identity", position = "dodge", colour = "black", fill = c("#49997c", "#ae3918", "#d19c2f" )) +
  geom_errorbar(aes(ymax=fit+se,ymin=fit-se),position=position_dodge(.9),width=0.2)+
  theme_bw(base_size = 17)+
  theme(legend.position="none") +
  xlab("Treatment")+
  ylab("Nitrogen (%)") 
```

delta 13C models
```{r}
dc1 <-lmer(delta.c ~ trt + (1|site/plot), na.action=na.exclude, data = fol)
anova(dc1)
dc2 <-lmer(delta.c ~ 1 + (1|site/plot), na.action=na.exclude, data = fol)
anova(dc1, dc2)

plot(dc1)
r.squaredGLMM(dc1)
summary(dc1)
```
deltaC13 is controlled by treatment

delta 13C means
```{r}
fol.trt1 =  emmeans(dc1, "trt")
emmeans(dc1, ~ trt )
emmeans(dc1, pairwise ~ trt)
plot(fol.trt1, comparisons = TRUE)
```

graph delta 13C
```{r}
plot(allEffects(dc1))
trt.th <- Effect("trt", dc1, xlevels=500)
trt.th=as.data.frame(trt.th)

#home made box plot
ggplot(trt.th, aes(x=trt, fit, color=trt, fill = trt)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
   geom_jitter(data=fol, aes(x = trt, y= delta.c, fill = trt, color =  trt), alpha = 0.2, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab(expression(""*paste(delta^{13}, "C (‰)"))) +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))

ggplot(trt.th, aes(x= trt, y=fit, fill = trt)) + 
  geom_bar(stat = "identity", position = "dodge", colour = "black", fill = c("#49997c", "#ae3918", "#d19c2f" )) +
  geom_errorbar(aes(ymax=fit+se,ymin=fit-se),position=position_dodge(.9),width=0.2)+
  theme_bw(base_size = 17)+
  theme(legend.position="none") +
 xlab("Treatment") +
  ylab(expression(""*paste(delta^{13}, "C (‰)"))) +
  scale_color_manual(values=wes_palette(n=3, name="Darjeeling1")) +
  scale_y_reverse()
```

delta 15 N model
```{r}
dn1 <-lmer(delta.n ~ trt +  (1|site/plot), na.action=na.exclude, data = fol)
dn2 <-lmer(delta.n ~ 1 + (1|site/plot), na.action=na.exclude, data = fol)
anova(dn1, dn2)
anova(dn1)

plot(dn1)
r.squaredGLMM(dn1)
summary(dn1)
```

```{r}
plot(allEffects(dn1))
trt.nn <- Effect("trt", dn1, xlevels=500)
trt.nn=as.data.frame(trt.nn)

#home made box plot
ggplot(trt.nn, aes(x=trt, fit, color=trt, fill = trt)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
   geom_jitter(data=fol, aes(x = trt, y= delta.n, fill = trt, color =  trt), alpha = 0.2, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab(expression(""*paste(delta^{15}, "N (‰)"))) +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))
```

delta 15N means
```{r}
fol.trt2 =  emmeans(dn1, "trt")
emmeans(dn1, ~ trt )
emmeans(dn1, pairwise ~ trt)
plot(fol.trt2, comparisons = TRUE)
```

foliar CN
```{r}
cn <-lmer(CN ~ trt + (1|site/plot), na.action=na.exclude, data = fol)
cn1 <-lmer(CN ~ 1  + (1|site/plot), na.action=na.exclude, data = fol)
anova(cn, cn1)
anova(cn)

plot(cn)
r.squaredGLMM(cn)
summary(cn)
```

```{r}
plot(allEffects(cn))
trt.ccnn <- Effect("trt", cn, xlevels=500)
trt.ccnn=as.data.frame(trt.ccnn)

#home made box plot
ggplot(trt.ccnn, aes(x=trt, fit, color=trt, fill = trt)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
   geom_jitter(data=fol, aes(x = trt, y= CN, fill = trt, color =  trt), alpha = 0.2, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab("C:N") +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))
```

=====================
=====================
environmental preds
```{r}
preds = read.csv("PerdyPred.csv")

preds$trt = factor(preds$trt, levels = c("unburned", "burn", "burn/sub"), labels= c("Unburned", "Burned", "Subsided"))
```

soil depth
```{r}
sol.m <-lmer(soil ~ trt +  (1|site), na.action=na.exclude, data = preds)
sol.m1 <-lmer(soil ~ 1 +  (1|site), na.action=na.exclude, data = preds)
anova(sol.m, sol.m1)
anova(sol.m)
plot(sol.m)
r.squaredGLMM(sol.m)
summary(sol.m)
```

```{r}
emmeans(sol.m, "trt")
emmeans(sol.m, pairwise ~ trt)
pair =  emmeans(ton.m, "trt")
plot(pair, comparisons = TRUE)
```

```{r}
#plotted with model outputs
plot(allEffects(sol.m))
ef.sol <- Effect(c("trt"), sol.m, xlevels=500)
ef.sol=as.data.frame(ef.sol)

#home made box plot
ggplot(ef.sol, aes(x= trt, y=fit, fill = trt, color= trt)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
 geom_jitter(data=preds, aes(x = trt, y=soil, fill = trt, color = trt), alpha = 0.2, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab("Soil organic layer depth (cm)") +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))

#bar plot
ggplot(ef.sol, aes(x= trt, y=fit, fill = trt)) + 
  geom_bar(stat = "identity", position = "dodge", colour = "black", fill = c("#49997c", "#ae3918", "#d19c2f" )) +
  geom_errorbar(aes(ymax=fit+se,ymin=fit-se),position=position_dodge(.9),width=0.2)+
 # geom_jitter(data=preds, aes(x = trt, y=soil, fill = trt, color = trt), alpha = 0.5, width = 0.3) +
  theme_bw(base_size = 17)+
   theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab("Soil organic layer depth (cm)") +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))
```

thaw depth
```{r}
thaw.m <-lmer(thaw ~ trt +  (1|site), na.action=na.exclude, data = preds)
thaw.m1 <-lmer(thaw ~ 1 +  (1|site), na.action=na.exclude, data = preds)
anova(thaw.m, thaw.m1)
anova(thaw.m)
plot(thaw.m)
r.squaredGLMM(thaw.m)
summary(thaw.m)
```

```{r}
trt2 =  emmeans(thaw.m, "trt")
emmeans(thaw.m, ~ trt )
emmeans(thaw.m, pairwise ~ trt)
plot(trt2, comparisons = TRUE)
```

```{r}
plot(allEffects(thaw.m))
ef.th <- Effect(c("trt"), thaw.m, xlevels=500)
ef.th=as.data.frame(ef.th)

#home made box plot
ggplot(ef.th, aes(x= trt, y=fit, fill = trt, color= trt)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
 geom_jitter(data=preds, aes(x = trt, y=thaw, fill = trt, color = trt), alpha = 0.2, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
 scale_y_reverse() +
   xlab("Disturbance catagory") +
  ylab("Thaw depth (cm)") +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))

ggplot(ef.th, aes(x= trt, y=fit, fill = trt)) + 
  geom_bar(stat = "identity", position = "dodge", colour = "black", fill = c("#49997c", "#ae3918", "#d19c2f" )) +
  geom_errorbar(aes(ymax=fit+se,ymin=fit-se),position=position_dodge(.9),width=0.2)+
  #geom_jitter(data=preds, aes(x = trt, y=thaw, fill = trt, color = trt), alpha = 0.5, width = 0.3) +
  theme_bw(base_size = 17)+
   theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
 scale_y_reverse() +
   xlab("Disturbance catagory") +
  ylab("Thaw depth (cm)") +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))
```

tape subsidence
```{r}
sub.m <-lmer(sub ~ trt +  (1|site), na.action=na.exclude, data = preds)
sub.m1 <-lmer(thaw ~ 1 +  (1|site), na.action=na.exclude, data = preds)
anova(sub.m, sub.m1)
anova(sub.m)
plot(sub.m)
r.squaredGLMM(sub.m)
summary(sub.m)
```

```{r}
emmeans(sub.m, "trt")
emmeans(sub.m, pairwise ~ trt)
pair =  emmeans(sub.m, "trt")
plot(pair, comparisons = TRUE)
```

```{r}
plot(allEffects(sub.m))
ef.sub <- Effect(c("trt"), sub.m, xlevels=500)
ef.sub=as.data.frame(ef.sub)

#home made box plot
ggplot(ef.sub, aes(x= trt, y=fit, fill = trt, color= trt)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
 geom_jitter(data=preds, aes(x = trt, y=sub, fill = trt, color = trt), alpha = 0.2, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
 scale_y_reverse() +
  xlab("Disturbance catagory") +
  ylab("Subsidence (cm)") +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))

ggplot(ef.sub, aes(x= trt, y=fit, fill = trt)) + 
  geom_bar(stat = "identity", position = "dodge", colour = "black", fill = c("#49997c", "#ae3918", "#d19c2f" )) +
  geom_errorbar(aes(ymax=fit+se,ymin=fit-se),position=position_dodge(.9),width=0.2)+
  #geom_jitter(data=preds, aes(x = trt, y=thaw, fill = trt, color = trt), alpha = 0.5, width = 0.3) +
  theme_bw(base_size = 17)+
   theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
 scale_y_reverse() +
   xlab("Disturbance catagory") +
  ylab("Subsidence (cm)") +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))

```


ash subsidence
```{r}
ash.m <-lm(ash ~ trt, na.action=na.exclude, data = preds)
ash.m1 <-lm(ash ~ 1 , na.action=na.exclude, data = preds)
anova(ash.m, ash.m1)
anova(ash.m)
summary(ash.m)
r.squaredGLMM(ash.m)

sub2 =  emmeans(ash.m, "trt")
emmeans(ash.m, ~ trt )
emmeans(ash.m, pairwise ~ trt)
plot(ash.m, comparisons = TRUE)

preds1 = preds %>% 
  group_by(trt) %>% 
  summarize(mean = mean(ash, na.rm=TRUE)) %>% 
  group_by(trt)%>%
  summarize (ash1 = mean(mean),
            se = sd(mean)/sqrt(length(mean)))

ggplot(preds1, aes(x= trt, y=ash1)) + 
   geom_bar(stat = "identity", position = "dodge", colour = "black", fill = c("#49997c", "#ae3918", "#d19c2f" )) +
  geom_errorbar(aes(ymax=ash1+se,ymin=ash1-se),position=position_dodge(.9),width=0.2)+
  scale_y_reverse()+
   theme_bw(base_size = 17)+
   theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab("Subsidence (cm)")
```

salix twig growth = not significant
```{r}
g.m <-lmer(growth ~ trt +  (1|site), na.action=na.exclude, data = preds)
g.m1 <-lmer(growth ~ 1 +  (1|site), na.action=na.exclude, data = preds)
anova(g.m, g.m1)
plot(g.m1)
r.squaredGLMM(g.m1)
summary(g.m)
```
