---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(MuMIn)
library(nlme)
library(effects)
library(influence.ME)
library(car)
library(emmeans)
```

```{r}
cn = read.csv("soil_MS_sub.csv")

cn$treatment = factor(cn$treatment, levels = c("nothing", "burn", "sub"), labels= c("Unburned", "Burned", "Subsided"))

cn$treatment = as.factor(cn$treatment)
cn$depth = as.numeric(cn$depth)
```

```{r}
ggplot(cn, aes(y = c.stock, x = treatment)) +
geom_boxplot(size = 1) +
theme_bw(base_size = 17)
ggplot(cn, aes(y = n.stock, x = treatment)) +
geom_boxplot(size = 1) +
theme_bw(base_size = 17)
```

deep cores from surface no subsidence taken into account
```{r}
cp.m <-lmer(c.stock ~ depth * treatment + (1| label), na.action=na.exclude, data = cn)
cp.m1 <-lmer(c.stock ~ depth + treatment + (1| label), na.action=na.exclude, data = cn)
anova(cp.m, cp.m1)
cp.m2 <-lmer(c.stock ~ depth + (1| label), na.action=na.exclude, data = cn)
anova(cp.m2, cp.m1)
cp.m3 <-lmer(c.stock ~ 1 + (1| label), na.action=na.exclude, data = cn)
anova(cp.m2, cp.m3)

anova(cp.m2)
plot(cp.m2)
```
depth matters
have to GLM

```{r}
plot(allEffects(cp.m2))
r <- Effect(c("depth"), cp.m2, xlevels=500)
r=as.data.frame(r)

ggplot() +
geom_point(data = cn, aes(x = c.stock, y = depth)) +
  theme_bw(base_size = 17)+
theme(aspect.ratio=1, panel.grid.minor = element_blank()) +  
ylab("Depth (cm)") +
xlab(expression("C stocks (g "*paste(m^{2}* ")"))) +
scale_y_reverse() +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
geom_line(data=r, aes(y = depth, x = fit),linetype="solid", size=1)+
geom_ribbon(data=r, aes(x = fit, y = depth, xmax = upper, xmin=lower), alpha=0.2) 
```

nitrogen no subsidence
```{r}
n.m <-lmer(n.stock ~ depth * treatment + (1| label), na.action=na.exclude, data = cn)
n.m1 <-lmer(n.stock ~ depth + treatment + (1| label), na.action=na.exclude, data = cn)
anova(n.m, n.m1)
anova(n.m)
n.m2 <-lmer(n.stock ~ treatment + (1| label), na.action=na.exclude, data = cn)
anova(n.m2, n.m1)
n.m2 <-lmer(n.stock ~ 1 + (1| label), na.action=na.exclude, data = cn)

```
nothing significant


cummulative sum work from ash equivalent
```{r}
cn1 = cn %>%
  na.omit() %>%
  group_by(treatment, plot) %>% 
  mutate(c.stock.cum = cumsum(c.stock)) %>%
  mutate(n.stock.cum = cumsum(n.stock))

cn2 <- cn1[c(7, 15, 22, 30, 41, 54, 67), ]
```

c stock with subsidence
```{r}
tot.m <-lmer(c.stock.cum ~ treatment + (1| plot), na.action=na.exclude, data = cn2)
tot.m1 <-lmer(c.stock.cum ~ 1 + (1| plot), na.action=na.exclude, data = cn2)
anova(tot.m, tot.m1)
plot(tot.m)

ggplot(cn2, aes(y = c.stock.cum, x = treatment)) +
geom_boxplot(size = 1) +
theme_bw(base_size = 17)
```
C stock not significant

N stock with subsidence
```{r}
ton.m <-lm(n.stock.cum ~ treatment, na.action=na.exclude, data = cn2)
ton.m1 <-lm(n.stock.cum ~ 1, na.action=na.exclude, data = cn2)
anova(ton.m, ton.m1)
Anova(ton.m, ton.m1)
Anova(ton.m)

#plot(ton.m) this freezes R

ggplot(cn2, aes(y = n.stock.cum, x = treatment)) +
geom_boxplot(size = 1) +
theme_bw(base_size = 17)
```

```{r}
emmeans(ton.m, "treatment")
emmeans(ton.m, pairwise ~ treatment)
pair =  emmeans(ton.m, "treatment")
plot(pair, comparisons = TRUE)
```
ISOTOPES
neither isotope significant

d15N
```{r}
dn.m <-lmer(d15N ~ depth * treatment + (1| label), na.action=na.exclude, data = cn)
dn.m1 <-lmer(d15N ~ depth + treatment + (1| label), na.action=na.exclude, data = cn)
anova(dn.m, dn.m1)
dn.m2 <-lmer(d15N ~ depth + (1| label), na.action=na.exclude, data = cn)
anova(dn.m2, dn.m1)
anova(dn.m1)
plot(dn.m1)
```
dn.m1 depth and treatment matter separately
residuals look awful so look at GLMM

d15N GLMM
```{r}
d1 <- glmer(d15N ~ treatment * depth + (1| label),  family = Gamma(link="log"), data = cn)
d2 <- glmer(d15N ~ treatment + depth + (1| label),  family = Gamma(link="log"), data = cn)
anova(d1, d2)
Anova(d2)
d3 <- glmer(d15N ~ depth + (1| label),  family = Gamma(link="log"), data = cn)
anova(d3, d2)
d4 <- glmer(d15N ~ 1 + (1| label),  family = Gamma(link="log"), data = cn)
anova(d3, d4)
```
Nothing significant

```{r}
plot(allEffects(dc.m1))
eff.dc <- Effect(c("depth", "treatment"), dc.m1, xlevels=500)
eff.dc=as.data.frame(eff.dc)

ggplot() +
geom_point(data = din, aes(x = DIN.area, y = depth1, group = treatment, color = treatment)) +
  theme_bw(base_size = 17)+
theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +  
ylab("Depth (cm)") +
xlab(expression("DIN (mg "*paste(m^{2}* ")"))) +
scale_y_reverse() +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
geom_line(data=r, aes(y = depth1, x = exp(fit), group = treatment),linetype="solid", size=1)+
geom_ribbon(data=r, aes(y = depth1, xmax = exp(upper), xmin=exp(lower), group = treatment), alpha=0.2) +
  facet_wrap(~treatment)
```

d13C
```{r}
dc.m <-lmer(d13C ~ depth * treatment + (1| label), na.action=na.exclude, data = cn)
dc.m1 <-lmer(d13C ~ depth + treatment + (1| label), na.action=na.exclude, data = cn)
anova(dc.m, dc.m1)
dc.m2 <-lmer(d13C ~ depth + (1| label), na.action=na.exclude, data = cn)
anova(dc.m2, dc.m1)
dc.m3 <-lmer(d13C ~ 1 + (1| label), na.action=na.exclude, data = cn)
anova(dc.m2, dc.m3)
```
Nothing matters


Check with shallow soils
```{r}
shal = read.csv("soil_MS_shal.csv")

shal$treatment = factor(shal$treatment, levels = c("nothing", "burn", "sub"), labels= c("Unburned", "Burned", "Subsided"))

shal$treatment = as.factor(shal$treatment)
shal$depth = as.numeric(shal$depth)
```

```{r}
ggplot(shal, aes(y = c.stock, x = treatment)) +
geom_boxplot(size = 2) +
theme_bw(base_size = 17)
ggplot(shal, aes(y = n.stock, x = treatment)) +
geom_boxplot(size = 2) +
theme_bw(base_size = 17)
```

shallow wihtou subsidence
```{r}
scm <-lmer(c.stock ~ depth * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
scm1 <-lmer(c.stock ~ depth + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(scm, scm1)
anova(scm1)
scm2 <-lmer(c.stock ~ depth  + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(scm2, scm1)
scm3 <-lmer(c.stock ~ 1  + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(scm2, scm3)
plot(scm3)
```
nothing matters

N stock without subsidence
```{r}
ns <-lmer(n.stock ~ depth * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
ns1 <-lmer(n.stock ~ depth + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(ns, ns1)
anova(ns1)
ns2 <-lmer(n.stock ~ depth + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(ns2, ns1)
ns3 <-lmer(n.stock ~ 1 + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(ns2, ns3)
```
nothing matters


cummulative sum work from ash equivalent
```{r}
sh.sub = read.csv("soil_MS_shal_sub.csv")

sh.sub$treatment = factor(sh.sub$treatment, levels = c("nothing", "burn", "sub"), labels= c("Unburned", "Burned", "Subsided"))

sh.sub$treatment = as.factor(sh.sub$treatment)
sh.sub$depth = as.numeric(sh.sub$depth)

sub1 = sh.sub %>%
  na.omit() %>%
  group_by(treatment, plot, core) %>% 
  mutate(c.stock.cum = cumsum(c.stock)) %>%
  mutate(n.stock.cum = cumsum(n.stock))

write.csv(sub1, file = "shal_sub_cum.csv")
```

cumm without top 5 cm in burned areas
```{r}
no.top = read.csv("soil_MS_shal_sub_notop.csv")

no.top$treatment = factor(no.top$treatment, levels = c("nothing", "burn", "sub"), labels= c("Unburned", "Burned", "Subsided"))

no.top$treatment = as.factor(no.top$treatment)
no.top$depth = as.numeric(no.top$depth)

no.top1 = no.top %>%
  na.omit() %>%
  group_by(treatment, plot, core) %>% 
  mutate(c.stock.cum = cumsum(c.stock)) %>%
  mutate(n.stock.cum = cumsum(n.stock))

write.csv(no.top1, file = "shal_sub_cum_notop.csv")
```

----------------------------------------
----------------------------------------
used in paper
subsidence and no regrowth
no.top2
```{r}
no.top2 = read.csv("shal_sub_cum_notop_back.csv")
no.top2$treatment = factor(no.top2$treatment, levels = c("Unburned", "Burned", "Subsidence"), labels= c("Unburned", "Burned", "Subsided"))

cc.m <-lmer(c.stock.cum ~ treatment + (1| site/plot), na.action=na.exclude, data = no.top2)
cc.m1 <-lmer(c.stock.cum ~ 1 + (1| site/plot), na.action=na.exclude, data = no.top2)
anova(cc.m, cc.m1)
plot(cc.m)

r.squaredGLMM(cc.m)
summary(cc.m)
Anova(cc.m)
```

outliers
```{r}
cc.m.lm <-lm(c.stock.cum ~ treatment, na.action=na.exclude, data = no.top2)
plot(cc.m.lm)
```

```{r}
emmeans(cc.m, "treatment")
emmeans(cc.m, pairwise ~ treatment)
pair =  emmeans(cc.m, "treatment")
plot(pair, comparisons = TRUE)
```

```{r}
ggplot(no.top2, aes(y = c.stock.cum, x = treatment)) +
geom_boxplot(size = 1) +
theme_bw(base_size = 17)

plot(allEffects(cc.m))
e.top <- Effect(c("treatment"), cc.m, xlevels=500)
e.top=as.data.frame(e.top)

#home made box plot
ggplot(e.top, aes(x=treatment, y=fit, color = treatment, fill = treatment)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
 geom_jitter(data=no.top2, aes(x = treatment, y= c.stock.cum, fill = treatment, color = treatment), alpha = 0.3, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab(expression("Carbon pools (g "*paste(m^{2}, ")"))) +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))
```

cummulative C stock with subsidence
```{r}
sub2 = read.csv("shal_sub_cum_back.csv")
sub2$treatment = factor(sub2$treatment, levels = c("Unburned", "Burned", "Subsidence"), labels= c("Unburned", "Burned", "Subsided"))

ccc <-lmer(c.stock.cum ~ treatment + (1| site/plot), na.action=na.exclude, data = sub2)
ccc1 <-lmer(c.stock.cum ~ 1 + (1| site/plot), na.action=na.exclude, data = sub2)
anova(ccc, ccc1)
plot(ccc)

r.squaredGLMM(ccc)
```
treatment matters

```{r}
emmeans(ccc, "treatment")
emmeans(ccc, pairwise ~ treatment)
pair =  emmeans(ccc, "treatment")
plot(pair, comparisons = TRUE)
```

plot model with raw jitter
```{r}
ggplot(sub2, aes(y = c.stock.cum, x = treatment)) +
geom_boxplot(size = 1) +
theme_bw(base_size = 17)

plot(allEffects(ccc))
ef.cs <- Effect(c("treatment"), ccc, xlevels=500)
ef.cs=as.data.frame(ef.cs)

#home made box plot
ggplot(ef.cs, aes(x=treatment, y=fit, color = treatment, fill = treatment)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
 geom_jitter(data=sub2, aes(x = treatment, y= c.stock.cum, fill = treatment, color = treatment), alpha = 0.3, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Treatment") +
  ylab(expression("Carbon stocks (g "*paste(m^{2}, ")"))) +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))
```

cummulative N pools
```{r}
nn.m <-lmer(n.stock.cum ~ treatment + (1| site/plot), na.action=na.exclude, data = no.top2)
nn.m1 <-lmer(n.stock.cum ~ 1 + (1| site/plot), na.action=na.exclude, data = no.top2)
anova(nn.m, nn.m1)
r.squaredGLMM(nn.m)
plot(nn.m)
summary(nn.m)
```
treament matters
```{r}
emmeans(nn.m, "treatment")
emmeans(nn.m, pairwise ~ treatment)
pair =  emmeans(nn.m, "treatment")
plot(pair, comparisons = TRUE)
```

plot model with raw jitter
```{r}
ggplot(no.top2, aes(y = n.stock.cum, x = treatment)) +
geom_boxplot(size = 1) +
theme_bw(base_size = 17)

plot(allEffects(nn.m))
en <- Effect(c("treatment"), nn.m, xlevels=500)
en =as.data.frame(en)

#home made box plot
ggplot(en, aes(x=treatment, y=fit, color = treatment, fill = treatment)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
 geom_jitter(data=no.top2, aes(x = treatment, y= n.stock.cum, fill = treatment, color = treatment), alpha = 0.3, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab(expression("Nitrogen pools (g  "*paste(m^{2}, ")"))) +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))
``` 

```{r}
nnn <-lmer(n.stock.cum ~ treatment + (1| site/plot), na.action=na.exclude, data = sub2)
nnn1 <-lmer(n.stock.cum ~ 1 + (1| site/plot), na.action=na.exclude, data = sub2)
anova(nnn, nnn1)
r.squaredGLMM(nnn)
```
treament matters
```{r}
emmeans(nnn, "treatment")
emmeans(nnn, pairwise ~ treatment)
pair =  emmeans(nnn, "treatment")
plot(pair, comparisons = TRUE)
```

plot model with raw jitter
```{r}
ggplot(sub2, aes(y = n.stock.cum, x = treatment)) +
geom_boxplot(size = 1) +
theme_bw(base_size = 17)

plot(allEffects(nnn))
ef.nn <- Effect(c("treatment"), nnn, xlevels=500)
ef.nn =as.data.frame(ef.nn)

#home made box plot
ggplot(ef.nn, aes(x=treatment, y=fit, color = treatment, fill = treatment)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
 geom_jitter(data=sub2, aes(x = treatment, y= n.stock.cum, fill = treatment, color = treatment), alpha = 0.3, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab(expression("Nitrogen stocks (g "*paste(m^{2}, ")"))) +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))
``` 

Shallow ISOTOPES
```{r}
ddd <-lmer(d15N ~ depth * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
ddd1 <-lmer(d15N ~ depth + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(ddd, ddd1)
anova(ddd1)
ddd2 <-lmer(d15N ~ depth + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(ddd1, ddd2)
ddd3 <-lmer(d15N ~ 1 + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(ddd3, ddd2)

plot(ddd2)
r.squaredGLMM(ddd2)
summary(ddd2)
```
depth matters

```{r}
plot(allEffects(ddd2))
eff.nit <- Effect(c("depth"), ddd2, xlevels=500)
eff.nit=as.data.frame(eff.nit)

ggplot() +
geom_point(data = shal, aes(x = d15N, y = depth,)) +
  theme_bw(base_size = 17)+
theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +  
ylab("Depth (cm)") +
xlab(expression(""*paste(delta^{15}, "N (‰)"))) +
scale_y_reverse() +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
geom_line(data=eff.nit, aes(y = depth, x = fit),linetype="solid", size=1)+
geom_ribbon(data=eff.nit, aes(y = depth, xmax = upper, xmin=lower), alpha=0.2)
```

```{r}
aaa <-lmer(d13C ~ depth * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
aaa1 <-lmer(d13C ~ depth + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(aaa, aaa1)
anova(aaa)

plot(aaa)
r.squaredGLMM(aaa)
summary(aaa)

coef(summary(aaa))[ , "Estimate"]
```
depth treatment interaction
unburned diff from burn and sub. unburned more depleted at surface

```{r}
emmeans(aaa, "treatment")
emmeans(aaa, pairwise ~ treatment)
pair =  emmeans(aaa, "treatment")
plot(pair, comparisons = TRUE)
```

```{r}
plot(allEffects(aaa))
eff.13 <- Effect(c("depth", "treatment"), aaa, xlevels=500)
eff.13=as.data.frame(eff.13)

ggplot() +
geom_point(data = shal, aes(x = d13C, y = depth, group = treatment, color = treatment)) +
  theme_bw(base_size = 17)+
theme(aspect.ratio=1, panel.grid.minor = element_blank()) +  
ylab("Depth (cm)") +
xlab(expression(""*paste(delta^{13}, "C (‰)"))) +
scale_y_reverse() +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
geom_line(data=eff.13, aes(y = depth, x = fit, group = treatment),linetype="solid", size=1)+
geom_ribbon(data=eff.13, aes(y = depth, xmax = upper, xmin=lower, group = treatment), alpha=0.2)
```

C/N to look at properties
```{r}
rat.m <-lmer(C.N ~ depth * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
rat.m1 <-lmer(C.N ~ depth + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(rat.m, rat.m1)
r.squaredGLMM(rat.m)
plot(rat.m)
summary(rat.m)
```
depth treatment interaction
ratio higher in unburned surface. = more C available

```{r}
emmeans(rat.m, "treatment")
emmeans(rat.m, pairwise ~ treatment)
pair =  emmeans(rat.m, "treatment")
plot(pair, comparisons = TRUE)
```

```{r}
plot(allEffects(rat.m))
eff.rat <- Effect(c("depth", "treatment"), rat.m, xlevels=500)
eff.rat=as.data.frame(eff.rat)

ggplot() +
geom_point(data = shal, aes(x = C.N, y = depth, group = treatment, color = treatment)) +
  theme_bw(base_size = 17)+
theme(aspect.ratio=1, panel.grid.minor = element_blank()) +  
ylab("Depth (cm)") +
xlab(expression("C:N")) +
scale_y_reverse() +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
geom_line(data=eff.rat, aes(y = depth, x = fit, group = treatment),linetype="solid", size=1)+
geom_ribbon(data=eff.rat, aes(y = depth, xmax = upper, xmin=lower, group = treatment), alpha=0.2)
```

-------------------------------
------------------------------
used in paper


shallow isotopes no top in burned area
```{r}
shal = read.csv("soil_MS_shal.csv")
shal$treatment = factor(shal$treatment, levels = c("nothing", "burn", "sub"), labels= c("Unburned", "Burned", "Subsided"))

top.m <-lmer(d15N ~ depth.sub * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
top.m1 <-lmer(d15N ~ depth.sub + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(top.m, top.m1)
anova(top.m)

plot(top.m)
r.squaredGLMM(top.m)
summary(top.m)
```

```{r}
emmeans(top.m, "treatment")
emmeans(top.m, pairwise ~ treatment)
pair =  emmeans(top.m, "treatment")
plot(pair, comparisons = TRUE)
```

```{r}
plot(allEffects(top.m))
e.del <- Effect(c("depth.sub", "treatment"), top.m, xlevels=500)
e.del=as.data.frame(e.del)

ggplot() +
geom_point(data = shal, aes(x = d15N, y = depth.sub, group = treatment, fill = treatment, color = treatment)) +
  theme_bw(base_size = 17)+
theme(aspect.ratio=1, panel.grid.minor = element_blank()) +  
ylab("Depth (cm)") +
xlab(expression(""*paste(delta^{15}, "N (‰)"))) +
scale_y_reverse() +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
geom_line(data=e.del, aes(y = depth.sub, x = fit, group = treatment),linetype="solid", size=1)+
geom_ribbon(data=e.del, aes(y = depth.sub, xmax = upper, xmin=lower, group = treatment), alpha=0.2) 
# +  labs(color = "Disturbance catagory")
```

```{r}
ct.m <-lmer(d13C ~ depth.sub * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
ct.m1 <-lmer(d13C ~ depth.sub + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(ct.m, ct.m1)
anova(ct.m)

plot(ct.m)
r.squaredGLMM(ct.m)
summary(ct.m)
```

```{r}
emmeans(ct.m, "treatment")
emmeans(ct.m, pairwise ~ treatment)
pair =  emmeans(ct.m, "treatment")
plot(pair, comparisons = TRUE)
```

```{r}
plot(allEffects(ct.m))
e.cth <- Effect(c("depth.sub", "treatment"), ct.m, xlevels=500)
e.cth=as.data.frame(e.cth)

ggplot() +
geom_point(data = shal, aes(x = d13C, y = depth.sub, group = treatment, fill = treatment, color = treatment), size = 3) +
  theme_bw(base_size = 17)+
theme(aspect.ratio=1, panel.grid.minor = element_blank()) +  
ylab("Depth (cm)") +
xlab(expression(""*paste(delta^{13}, "C (‰)"))) +
scale_y_reverse() +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
  scale_fill_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
geom_line(data=e.cth, aes(y = depth.sub, x = fit, group = treatment, color = treatment),linetype="solid", size=1)+
geom_ribbon(data=e.cth, aes(y = depth.sub, xmax = upper, xmin=lower, group = treatment), alpha=0.2)
```

```{r}
cn.m <-lmer(C.N ~ depth.sub * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
cn.m1 <-lmer(C.N ~ depth.sub + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(cn.m, cn.m1)
anova(cn.m)

plot(cn.m)
r.squaredGLMM(cn.m)
summary(cn.m)
```

```{r}
emmeans(cn.m, "treatment")
emmeans(cn.m, pairwise ~ treatment)
pair =  emmeans(cn.m, "treatment")
plot(pair, comparisons = TRUE)
```

```{r}
plot(allEffects(ct.m))
e.cn <- Effect(c("depth.sub", "treatment"), cn.m, xlevels=500)
e.cn=as.data.frame(e.cn)

ggplot() +
geom_point(data = shal, aes(x = C.N, y = depth.sub, group = treatment, fill = treatment, color = treatment)) +
  theme_bw(base_size = 17)+
theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +  
ylab("Depth (cm)") +
xlab("C:N") +
scale_y_reverse() +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
geom_line(data=e.cn, aes(y = depth.sub, x = fit, group = treatment),linetype="solid", size=1)+
geom_ribbon(data=e.cn, aes(y = depth.sub, xmax = upper, xmin=lower, group = treatment), alpha=0.2)
```

```{r}
carb.m <-lmer(C ~ depth.sub * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
carb.m1 <-lmer(C.N ~ depth.sub + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(carb.m, carb.m1)
anova(carb.m1)
carb.m2 <-lmer(C.N ~ treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(carb.m2, carb.m1)
carb.m3 <-lmer(C.N ~ 1 + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(carb.m2, carb.m3)


plot(carb.m2)
r.squaredGLMM(carb.m2)
summary(carb.m2)
```

```{r}
emmeans(carb.m2, "treatment")
emmeans(carb.m2, pairwise ~ treatment)
pair =  emmeans(carb.m2, "treatment")
plot(pair, comparisons = TRUE)
```


```{r}
plot(allEffects(carb.m2))
e.carb <- Effect(c("treatment"), carb.m2, xlevels=500)
e.carb=as.data.frame(e.carb)

#home made box plot
ggplot(e.carb, aes(x=treatment, y=fit, color = treatment, fill = treatment)) + 
  geom_point(size = 3) + 
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), size = 1, width=0.25) + 
 geom_jitter(data=shal, aes(x = treatment, y= C, fill = treatment, color = treatment), alpha = 0.3, width = 0.1) +
  theme_bw(base_size = 17)+
  theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +
  xlab("Disturbance catagory") +
  ylab("C (‰)") +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" )))
```

```{r}
nit.m <-lmer(N ~ depth.sub * treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
nit.m1 <-lmer(C.N ~ depth.sub + treatment + (1| site/plot/core), na.action=na.exclude, data = shal)
anova(nit.m, nit.m1)
anova(nit.m)

plot(nit.m)
r.squaredGLMM(nit.m)
summary(nit.m)
```

```{r}
emmeans(nit.m, "treatment")
emmeans(nit.m, pairwise ~ treatment)
pair =  emmeans(nit.m, "treatment")
plot(pair, comparisons = TRUE)
```

```{r}
plot(allEffects(nit.m))
e.nit <- Effect(c("depth.sub", "treatment"), nit.m, xlevels=500)
e.nit=as.data.frame(e.nit)

ggplot() +
geom_point(data = shal, aes(x = N, y = depth.sub, group = treatment, fill = treatment, color = treatment)) +
  theme_bw(base_size = 17)+
theme(aspect.ratio=1, panel.grid.minor = element_blank(), legend.position="none") +  
ylab("Depth (cm)") +
xlab("N (‰)") +
scale_y_reverse() +
  scale_color_manual(values=c(c("#49997c", "#ae3918", "#d19c2f" ))) +
geom_line(data=e.nit, aes(y = depth.sub, x = fit, group = treatment),linetype="solid", size=1)+
geom_ribbon(data=e.nit, aes(y = depth.sub, xmax = upper, xmin=lower, group = treatment), alpha=0.2)
```
